Think deep for reef resilience

### 2025-08-08 paper/paper_draft.qmd
Add reference to figure

The spatial extent of the GBR reefs represented in this investigation follows the reef
definitions available via the Great Barrier Reef Marine Park Authority [@greatba2022]. In
total, the dataset represents 3806 reef areas across the GBR marine park. Reefs that are
outside the GBRMPA management areas or are not associated with a GBRMPA reefal bioregion
were removed from the investigation, leaving 3531 reefs. Annually and spatially averaged
Degree Heating Week (DHW) data were used to represent future thermal stress at each reef
location. Code used to calculate DHW data and perform analyses involved in this
investigation can be found at **insert repo citation**.

>>>>

The spatial extent of the GBR reefs represented in this investigation follows the reef
definitions available via the Great Barrier Reef Marine Park Authority [@greatba2022]. An
indicative map of the GBR marine park including the Marine Park regions and which bioregion
each reef belongs to is shown in @fig-region-map. In total, the dataset represents 3806 reef
areas across the GBR marine park. Reefs that are outside the GBRMPA management areas or are
not associated with a GBRMPA reefal bioregion **\[TI: Ben, cite the bioregion data
source\]** were removed from the investigation, leaving 3531 reefs. Annually and spatially
averaged Degree Heating Week (DHW) data were used to represent future thermal stress at each
reef location. Code used to calculate DHW data and perform analyses involved in this
investigation can be found at **insert repo citation**.
